### 2011-08-15 doc/theses/vitasek/diplomka.tex
Thesis: in progress.

@@

@@

\begin{table}
  \caption{GLPK: native vs. Cygwin summary 1}
  \label{experiment-glpk-native-vs-cygwin-summary-1}
  \centering
  \begin{tabular}{| l | l |}
  \hline
  Machine           & Windows \\
  Input data set    & \texttt{100-500} \\
  Iterations        & 20 \\
  Pool size         & 1 \\
  $\alpha$, $\beta$ & $1$, $1$ \\
  \hline
  \end{tabular}
\end{table}

@@

\begin{table}
  \caption{GLPK: native vs. Cygwin summary 2}
  \label{experiment-glpk-native-vs-cygwin-summary-2}
  \centering
  \begin{tabular}{| l | l |}
  \hline
  Machine           & Windows \\
  Input data set    & sized artificial data \\
  Iterations        & 20 \\
  Pool size         & 1 \\
  $\alpha$, $\beta$ & $1$, $1$ \\
  \hline
  \end{tabular}
\end{table}

@@

\begin{algorithm}
\caption{GLPK: native vs. Cygwin set generation 2}
\label{listing-experiment-glpk-native-vs-cygwin-2}
\begin{algorithmic}
\ENSURE experimental set $ES$
\STATE $ES \gets \emptyset$
\FOR{$i = 1 \to 20$}
	\FOR{$file \in $ sized artificial data}
    \STATE $ES \gets ES \cup {file, CH = \jmodule{Glpk}(no limit), IH = \emptyset}$  
  \ENDFOR
\ENDFOR
\RETURN $ES$
\end{algorithmic}
\end{algorithm}

@@

\begin{itemize}
	\item For each input file: how long does model creation take?
	\item How long does it take to communicate with GLPK? Creating the input / parsing the output.
	\item Which construction heuristic is the best - limit GLPK to like 1 second
	\item With the best construction heuristic, which IH is the best? Note that this needn't be the best combination!
	\item With the best IH from the previous step, how about using Random as CH?
	\item GLPK: Input -> How long the search for optimum lasts - this shows we cannot rely on GLPK alone! it just takes too long.
	\item GLPK: Time limit -> Quality
	\item Structure of the data -> Which algorithms perform the best
	\item Alpha, Beta -> Quality
	\item Alpha, Beta -> How does the solution work?
	\item Do I beat FIDAX with Random?
	\item Does Fuzzy beat Random? (Fuzzy wins in every single case) - take note of quality (mean, variance) but also time (again, mean)
  \item Can FIDAX be improved by Hungry?
  \item Can we improve performance on huge data by ignoring textual content? Check for building as well as actual heu times.
\end{itemize}

>>>>

\subsection{Grammar and model generation}

%         NB class GrammarModelTiming

TODO in this experiment we shall see how long it takes to create the IG and the model. So far, this is isolated from heus themselves.

The first experiment set will try to establish how long it takes to extract the IG % TODO IG -> nomenclature
from the input XML file and how long does it take to create the AM model from this IG. For now, we will not be running or measuring any heuristics.

\begin{tabular}{| l | l |}
  \hline
  \hline
  Machine           & TODO \\
  Input data set    & all test data sets \\
  Iterations        & 20 \\
  Pool size         & not applicable \\
  $\alpha$, $\beta$ & not applicable \\
  \hline
\end{tabular}

The experimental set will contain $20 * (11 + 11) = 440$ configurations - 20 iterations for 11 test data sets plus 11 sized test data sets. There won't be any CHs or IHs. We will be gathering the timing data for IG extraction and model generation in GnuPlot format.

@@

%         NB class TimeQuality

@@

\begin{tabular}{| l | l |}
  \hline
  \hline
  Machine           & Windows \\
  Input data set    & \texttt{100-500} \\
  Iterations        & 20 \\
  Pool size         & 1 \\
  $\alpha$, $\beta$ & $1$, $1$ \\
  \hline
\end{tabular}

@@

\begin{tabular}{| l | l |}
  \hline
  \hline
  Machine           & Windows \\
  Input data set    & sized artificial data \\
  Iterations        & 20 \\
  Pool size         & 1 \\
  $\alpha$, $\beta$ & $1$, $1$ \\
  \hline
\end{tabular}

@@

\begin{algorithm}
\caption{GLPK: native vs. Cygwin set generation 2}
\label{listing-experiment-glpk-native-vs-cygwin-2}
\begin{algorithmic}
\ENSURE experimental set $ES$
\STATE $ES \gets \emptyset$
\FOR{$i = 1 \to 20$}
	\FOR{$file \in $ sized artificial data}
    \STATE $ES \gets ES \cup \{file, CH = \jmodule{Glpk}(no\:limit), IH = \emptyset\}$  
  \ENDFOR
\ENDFOR
\RETURN $ES$
\end{algorithmic}
\end{algorithm}

@@

\begin{itemize}
  \item How long does it take to communicate with GLPK? Creating the input / parsing the output.
  \item Big fight Fuzzy vs. Random vs. FIDAX take note of quality (mean, variance) but also time (again, mean)
  \item Can FIDAX be improved by Hungry?

	\item Which construction heuristic is the best - limit GLPK to like 1 second

	\item With the best construction heuristic, which IH is the best? Note that this needn't be the best combination!
	\item With the best IH from the previous step, how about using Random as CH?

  \item this can be done inside the GLPK version comparison! GLPK: Input -> How long the search for optimum lasts - this shows we cannot rely on GLPK alone! it just takes too long.
	\item this can be done inside the GLPK version comparison! GLPK: Time limit -> Quality

	\item Structure of the data -> Which algorithms perform the best

  \item Alpha, Beta -> Quality
	\item Alpha, Beta -> How does the solution work?

  \item Can we improve performance on huge data by ignoring textual content? Check for building as well as actual heu times.
\end{itemize}
